Examining Whether Approximate Visualizations Impact Perception of Corrected Visualizations

### 2016-12-09 paper/paper.tex
TODOs

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
\todo{The abstract goes here.}
\end{abstract}

@@

In this study we wanted to understand whether analysts have a bias in how they recall precise data.
Before we analyze the bias between what participants remembered from the approximate and precise visualizations, we look at the relative errors (absolute bias) independently.
We removed outliers where the relative bias was larger than 4 times the standard deviation using sigma clipping.
\tabref{table_errors} summarized the results.
Since we expect a bias (R1), the errors in the precise visualization should be larger.
The errors for the type 1 questions were significantly larger ($p=0.0002$ for type 1), while we could not see a significant effect of type 2 questions.  \todo{What's happening? These errors are waaaay too large.}

@@

\todo{mean and variance of measures and expected bias}

@@

Tie to crowdsourcing literature here, about what our work could inform over there \todo{when we have data}.

\todo{Explain why we see the bias}
\todo{Talk about massive error}

@@

\todo{Statistical methods and outliers}

@@

\todo{future research questions}

>>>>

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
\todo{Dom: The abstract goes here.}
\end{abstract}

@@

In this study we wanted to understand whether analysts have a bias in how they recall precise data.
Before we analyze the bias between what participants remembered from the approximate and precise visualizations, we look at the relative errors (absolute bias) independently.
We removed outliers where the relative bias was larger than 4 times the standard deviation using sigma clipping.
\tabref{table_errors} summarized the results.
Since we expect a bias (R1), the errors in the precise visualization should be larger.
The errors for the type 1 questions were significantly larger ($p=0.0002$ for type 1), while we could not see a significant effect of type 2 questions.  \todo{Dom: What's happening? These errors are waaaay too large.}

@@

\begin{table}[!t]
% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{The mean and standard deviation of the true and expected bias.}
\label{table_errors}
\centering
\begin{tabular}{|l||r|r|r|r|}
\hline
Question & Bias Type  & Mean  & Standard deviation \\ \hline
\hline
type 1   & true      &      &           \\ \hline
type 1   & expected  &      &           \\ \hline
type 2   & true      &      &           \\ \hline
type 2   & expected  &      &           \\ \hline
\end{tabular}
\end{table}

\todo{Daniel: mean and variance of measures and expected bias}

@@

\todo{Daniel: Explain why we see the bias}
\todo{Dom: Talk about massive error}

@@

\todo{Daniel: Statistical methods and outliers}
\todo{Dom: more threats}

@@
